CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-08 paper/ms.tex
fix bugs

\subsection{\label{sec:level2}Spectrum calibration}
\bigskip
After the optimization, we obtain many sets of a, b and c. In our theory b should be close to 1 and a, c is much smaller than b. But the fact is that sometimes b is close to -1. This is because of the spectral broadening in the measurement. The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons. Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1. Thus b will be close to -1 and at the same time a and c should be close to 1, which we will check in experiment 3.
\bigskip

Sometimes a or c will be close to 1. This is also because of the measurement. Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum. If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c. The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving. We will show this in experiment 4.
\bigskip

@@

In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.  What if we optimize more stars? We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot. The number of stars is 907. Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 907 objective functions. And there will be 907 sets of a, b and c.

@@

\bigskip
Now choose some examples from the 907 stars and make some plots.

@@

\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared}
\bigskip

@@

\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared}
\bigskip

@@

\centerline{Fig.7 Spectrum of the four stars with b closest to 1}
\bigskip

From the histogram of a, b and c, we also find that sometimes b becomes -1, which means the spectrum is broadened due to the measurement. The resolution of the spectrum becomes lower and this is what we want to calibrate.
\bigskip
Here is the plot of the four stars with b closest to -1:
\bigskip

@@

\centerline{Fig.8 Spectrum of the four stars with b closest to -1}
\bigskip

@@

We found a and c are close to 1, which is in accordance with our theory. 
Also, the optimized spectrum broaden when b =-1, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
\bigskip

@@

\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$}
\bigskip

@@

\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$}
\bigskip

@@

>>>>

\subsection{\label{sec:level2}Spectrum calibration}
\bigskip
After the optimization, we obtain many sets of a, b and c. In our theory b should be close to 1 and a, c is much smaller than b. But the fact is that sometimes b is much smaller than and c. This is because of the spectral broadening in the measurement. The equipment is not perfect, so the resolution of the spectrum will become lower due to scattering, dispersion or other reasons. Then the spectrum will broaden and the real spectrum at pixel j is not what we obtain, it should be the spectrum at nearby pixels, which include pixel j-1 and j+1. Thus b will be smaller than a+c, which we will discuss in the following experiment 3.
\bigskip

Sometimes a or c will be much bigger than the other two parameters. This is also because of the measurement. Even we ignore the spectral broadening, the measured spectrum may move one pixel left or one pixel right from the real spectrum. If the measured spectrum move one pixel left, then a should be close to 1 and it's similar for c. The measured spectrum moves left or right is because of the error in the measured velocity, so there will be error in measuring the Doppler effect, which leads to a spectrum moving. We will show this in experiment 3.
\bigskip

@@

In experiment 1, we use only four stars to obtain parameters a, b and c and the result is pretty good.  What if we optimize more stars? We randomly choose about 1\% of the APOGEE DR10 and make a histogram plot. The number of stars is 614. Now parameters a, b and c are obtained from independent stars, which means the objective function only contain the chi-squared of one star and there will be 614 objective functions. And there will be 614 sets of a, b and c.

@@

\bigskip
Now choose some examples from the 614 stars and make some plots.

@@

\centerline{Fig.5 Spectrum of the four stars with biggest delta-chi-squared. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

\centerline{Fig.6 Spectrum of the four stars with smallest delta-chi-squared. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

\centerline{Fig.7 Spectrum of the four stars with b closest to 1. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

From the histogram of a, b and c, we also find that sometimes b becomes much smaller than a+c, which means the spectrum is broadening due to the measurement. The resolution of the spectrum becomes lower and this is what we want to calibrate.
\bigskip
Here is the plot of the four stars with biggest a+c-b:
\bigskip

@@

\centerline{Fig.8 Spectrum of the four stars with biggest a+c-b. }

\centerline{The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

We found a and c are close to 1, which is in accordance with our theory. 
Also, the optimized spectrum broaden when a+c is much bigger than b, which means the measured spectrum broaden due to the error in the measurement. This is what we need to calibrate.
\bigskip

@@

\centerline{Fig.9 Spectrum of the four stars with biggest $a-c$.}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

\centerline{Fig.10 Spectrum of the four stars with biggest $c-a$.}

\centerline{ The black line is the observed spectrum. The green line is the inferred spectrum and the red line is the optimized spectrum.}
\bigskip

@@

  %% Fifth paragraph

 \section{\label{sec:level1}Appendix}

 Now we exclude stars with undetermined labels and re-plot the histogram of a, b and c.

\includegraphics[width=170mm]{d_figure_2.png}
\bigskip

\centerline{Fig.2 Histogram of a b c for apstar data (What we use now)}
\bigskip
